---
title: "Untitled"
output: html_document
date: '2022-09-17'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Midst a monsoon, another TokyoR meetup! Since the pandemic started all of TokyoR’s meetups have turned into online sessions and the transition has been seamless thanks to the efforts of the `TokyoR` organizing team. 

My previous TokyoR roundups:

- [Japan.R 2018 (12/1/2018)](https://ryo-n7.github.io/2018-12-06-japanr-conference-roundup-blog-post/)
- [Tokyo.R #76 (3/2/2019)](https://ryo-n7.github.io/2019-03-07-tokyoR-76-roundup/)
- [Tokyo.R #77 (4/13/2019)](https://ryo-n7.github.io/2019-04-24-tokyoR-77/)
- [Tokyo.R #78 (5/25/2019)](https://ryo-n7.github.io/2019-05-31-tokyoR-78-roundup/)
- [Tokyo.R #79 (6/29/2019)](https://ryo-n7.github.io/2019-07-05-tokyoR-79-roundup/)
- [Tokyo.R #80 (7/27/2019)](https://ryo-n7.github.io/2019-08-02-tokyoR-80-roundup/)
- [Tokyo.R #81 (9/28/2019)](https://ryo-n7.github.io/2019-10-30-tokyoR-81-roundup/)
- [Tokyo.R #87 (7/ /2020)](https://ryo-n7.github.io/2020-08-03-tokyoR-87-roundup/)

As you can see it was my first TokyoR in quite a long time, so it was nice to be back! On top of short summaries of all the talks I will also provide some helpful links and resources of my own to supplement the content of the talks.

Let's get started!

# BeginneR Session

As with every TokyoR meetup, we began with a set of beginner user focused talks: 

- [Intro to R - @kotatyamtema](https://www.slideshare.net/kotora_0507/tokyor101beginnerssession1pdf)
- [Data cleaning - @kotatyamtema](https://www.slideshare.net/kotora_0507/tokyor101beginnerssession2pdf)
- [Data visualization - @yutakanzawa](https://ytknzw.github.io/TokyoR/%E5%88%9D%E5%BF%83%E8%80%85%E3%82%BB%E3%83%83%E3%82%B7%E3%83%A7%E3%83%B3_%E3%83%87%E3%83%BC%E3%82%BF%E5%8F%AF%E8%A6%96%E5%8C%96_TokyoR_20220917.pdf)

# Main Session

## Data cleaning with Palmer penguins - @bob3bob3

```{r}
install.packages("palmerpenguins")
```

Data of 3 species of penguin

weight, wingspan, beak length, etc.


- penguins_raw: raw data set gathered from study
- penguins: cleaned version

- Goal: start with `penguins_raw` and get to `penguins`

```{r}
library(palmerpenguins)
library(summarytools)

penguins_raw |>
  dfSummary() |>
  View()
```


explore output from `dfSummary()`

- steps:

remove rows

clean values

recode factors into japanese


Next time he'll continueu this series as he plans on doing another talk on EDA and visualization, and then more planned talks on doing various statistical analysis on this data set.



### Resources

* [{palmerpenguins} R package](https://github.com/allisonhorst/palmerpenguins)
* [Intro to Palmer Penguins dataset: Twitter thread (Allison Horst)](https://twitter.com/allison_horst/status/1270046399418138625)


## Regression Analysis with R - @kilometer00

- [Slides](https://speakerdeck.com/kilometer/tokyor-number-101-regressionanalysis)

TokyoR organizer, `@kilometer00` gave a very thorough overview of regression analysis using R. From using the base `lm()` function, to going step-by-step to calculating the various statistical outputs (residuals, standard errors, F-statistic, etc.) manually, and concise explanations of all of the formulas behind them, this was a helpful intro for anybody trying to understand linear regression using R.

![]()

## Resources

- [Linear Models with R - Julian J. Faraway](https://www.utstat.toronto.edu/~brunner/books/LinearModelsWithR.pdf)
- [Extending the Linear Model with R - Julian J. Faraway](https://julianfaraway.github.io/faraway/ELM/)
- [Statistical Inference via Data Science: A ModernDive into R and the Tidyverse - Chester Ismay & Albert Y. Kim](https://moderndive.com/)

# Lightning Talks

## R and Snowflake - `@y__mattu`

R and RStudio author   `@y__mattu`



snowflake: data cloud service

"modern data stack": cloud data warehouse emergence


no R + Snowflake package


Connect via {odbc} and {DBI} R packages


install `unixodbc`  >>> snowflake driver 

connect via `dbiconnect()`

then send query

## Resources

- [](https://hevodata.com/learn/snowflake-r/)
- [](https://community.snowflake.com/s/article/How-To-Connect-Snowflake-with-R-RStudio-using-RODBC-driver-on-Windows-MacOS-Linux)

## Buying art with R - `@saltcooky`

- [Slides](https://speakerdeck.com/saltcooky12/rdeyou-ming-hui-hua-woan-quan-nimai-itai)

- Jackson Pollock artwork

fractal analysis of paintings

box-counting algorithm: `box_counting()`

## Resources

[{VoxR}: Trees Geometry and Morphology from Unstructured TLS Data - Bastien Lecigne](https://cran.r-project.org/package=VoxR)


## Graphs - `@bob3bob3`

In his 2nd presentation of the day, `@bob3bob3` talked about graphs, specifically some visualization functions that are included in base R. 

Why does R have these functions? ... [For compatibility with S](https://twitter.com/whydoesr).

For those that might not get the joke/adage/whatever, these visualization functions continued to exist in R due to its origins in its predecessor language, S.



- sunflower plots, face graph, 

`sunflowerplot()` function in base R!: https://statisticaloddsandends.wordpress.com/2021/02/05/what-is-a-sunflower-plot/

stem-and-leaf plot: `stem()` function in base R graphics


Chernoff face graph: {aplpack}::`faces()`

- https://flowingdata.com/2010/08/31/how-to-visualize-data-with-cartoonish-faces/

and provided an example using the Palmer penguins dataset that he used in his previous presentation.

![]()

Nowadays, for similar visualizations, people can make radar plots or parallel coordinate plots.

## Resources

- Schilling, M. F. and Watkins, A. E. (1994). A suggestion for sunflower plots. The American Statistician, 48, 303–305. doi: 10.2307/2684839.

- Hermann Chernoff (1973). The use of faces to represent points in k-dimensional space graphically. Journal of the American Statistical Association, 68(342), 361–368.

- [{aplpack}: 'Bagplots', 'Iconplots', 'Summaryplots', Slider Functions and Others - Hans Peter Wolf](https://cran.r-project.org/package=aplpack)

- [{ggChernoff}: Chernoff face geom for {ggplot2} - David Selby](https://cran.r-project.org/package=ggChernoff)



# Conclusion

The next TokyoR meetup is scheduled for sometime near the end of October. Please follow the [official Twitter account]() to keep tabs on any new updates. For the time being meetups will continue to be conducted online. Talks in English are also welcome so come join us!
